### 2019-05-20 index.Rmd
get links working correctly on pkgdown homepage

### *Joural of Open Souce Software* Article
An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/). The article includes benchmarking of `areal` performance on several data sets. Please [cite the paper](/docs/authors.html) if you use `areal` in your work!

### What is New in v0.1.4.5?
This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission. Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests! Check out the [Changelog](/docs/news/index.html) for details on all of the bugs that were identified.

>>>>

### *Joural of Open Souce Software* Article
An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/). The article includes benchmarking of `areal` performance on several data sets. Please [cite the paper](authors.html) if you use `areal` in your work!

### What is New in v0.1.4.5?
This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission. Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests! Check out the [Changelog](news/index.html) for details on all of the bugs that were identified.
